From Freebase to Wikidata: The Great Migration

### 2016-01-13 paper.tex
Switch to home made statement schema in order to simplify the legal process

A~statement is composed of a~claim and zero or more references for this claim.
The claim itself is composed of one main property--value pair that encodes
the main (claimed) fact like ``population is 8,173,900'' and optional qualifiers
to add information about it like ``as of June 2012''.
\autoref{fig:statement} illustrates the used terminology with an example.

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=8.45 cm]{img/Wikidata_statement.pdf}
  \caption{Wikidata terminology illustrated with an example (Source:
	\url{https://commons.wikimedia.org/wiki/File:Wikidata_statement.svg}).}
  \label{fig:statement}
\end{figure}

>>>>

A~statement is composed of a~claim and zero or more references for this claim.
The claim itself is composed of one main property--value pair that encodes
the main (claimed) fact like ``taxon name is Pantera Leo'' and optional qualifiers
to add information about it like ``taxon author is Carl Linnaeus''.
\autoref{fig:statement} illustrates the used terminology with an example.

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=8.45 cm]{img/wikidata-statement-schema.pdf}
  \caption{Wikidata statement terminology illustrated with an example.}
  \label{fig:statement}
\end{figure}
